Differential invariant signatures for planar Lie group transformations of images

### 2021-08-04 paper/newpaper.tex
As submitted
Some progress on ref reports

The methods we use to construct the invariants, particularly the moving frames, produces invariants that, when considered alone, are singular at points (such as critical points). However, in all groups considered the invariants are rational functions of the derivatives of the function. Moreover, the denominators of these functions are powers of each other, and so it is possible to clear them by a projection technique that will be introduced in Section~\ref{sec:Sim2}.

@@

\begin{figure}
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=.45\textwidth]{Figs/function_scanlines} &
  \includegraphics[width=.45\textwidth]{Figs/f_transformed_T2} \\
  (a) & (b) \\
  \includegraphics[width=.45\textwidth]{Figs/T2_signature} &
  \includegraphics[width=.45\textwidth]{Figs/T2_match} \\
  (c) & (d)
  \end{tabular}
  \caption{(a), (b) The image before and after the $T(2)$ transformation $(x,
  y) \mapsto (x + 0.1, y - 0.2)$. (c) the signature of the
  image (before translation). (d) the signatures before and after the
  translation superimposed.}\label{fig:T2}
\end{figure}

@@

The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models. Invariants for this group have been computing using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.

@@

For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
\begin{equation}
\label{eq:e2tensor}
\begin{aligned}
  I_0 &= f = f \\
  I_1 &= f_if_i = f_x^2 + f_y^2 \\
  I_2 &= f_{ii} = f_{xx} + f_{yy} \\
  I_3 &= f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}.
\end{aligned}
\end{equation}

@@

Under similarity transformations, the Euclidean invariants become
\emph{relative invariants}, i.e., each derivative introduces a multiple of $s$ to
each invariant. For example, $\bar{f}_{\bar x}^2 + \bar{f}_{\bar y}^2 =
s^2(f_x^2 + f_y^2)$ and $\bar{f}_{\bar x \bar x}^2 + 2\bar{f}_{\bar x \bar
y}^2 + \bar{f}_{\bar y \bar y} = s^4 (f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2$). We
refer to the power of $s$ as the weight of the transformation. The concept of a 
relative invariant will be important in the rest of this paper. It follows the 
definition given here, except that the function weighting the invariant is more 
general, see~\citet{Fels1997} for more details. In contrast to that paper, 
we will continue to use the term weight to represent the power to which the function is raised.

@@

Functions of these invariants are invariants or relative invariants for many groups that contain $E(2)$, such as those that we have considered in this paper.

>>>>

The methods we use to construct the invariants, particularly the moving frames, produce invariants that are singular at points such as critical points. In all groups considered the invariants are rational functions of the derivatives of the function. Moreover, the denominators of these functions are powers of each other, and so it is possible to clear the denominators, thereby removing the singularity, by a projection technique that will be introduced in Section~\ref{sec:Sim2}.

@@

\begin{figure}
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=.45\textwidth]{Figs/function_scanlines} &
  \includegraphics[width=.45\textwidth]{Figs/f_transformed_T2} \\
  (a) & (b) \\
  \includegraphics[width=.45\textwidth]{Figs/T2_signature} &
  \includegraphics[width=.45\textwidth]{Figs/T2_match} \\
  (c) & (d)
  \end{tabular}
  \caption{(a), (b) The image before and after the $T(2)$ transformation $(x,
  y) \mapsto (x + 0.1, y - 0.2)$. (c) the signature of the
  image (before translation). (d) the signatures before (blue) and after (red)
  the translation superimposed, showing that the signature surface is invariant.}\label{fig:T2}
\end{figure}

@@

The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models. Invariants for this group have been computed using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.

@@

For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
\begin{equation}
\label{eq:e2tensor}
\begin{aligned}
  I_0 &= f = f \,,\\
  I_1 &= f_if_i = f_x^2 + f_y^2  \,,\\
  I_2 &= f_{ii} = f_{xx} + f_{yy} \,,\\
  I_3 &= f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \,,\\
  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}\,.
\end{aligned}
\end{equation}

@@

Under transformations by $\text{Sim}(2)$, the Euclidean invariants become
\emph{relative} invariants, i.e., each derivative introduces a multiple of $s$ to
each invariant. For example, $\bar{f}_{\bar x}^2 + \bar{f}_{\bar y}^2 =
s^2(f_x^2 + f_y^2)$ and $\bar{f}_{\bar x \bar x}^2 + 2\bar{f}_{\bar x \bar
y}^2 + \bar{f}_{\bar y \bar y} = s^4 (f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2$). We
refer to the power of $s$ as the weight of the transformation. The concept of a 
relative invariant will be important in the rest of this paper. It follows the 
definition given here, except that the function weighting the invariant is more 
general, see~\citet{Fels1997} for more details. In contrast to that paper, 
we will continue to use the term weight to represent the power to which the function is raised.

@@

Functions of these invariants are invariants or relative invariants for many groups that contain $E(2)$, such as those that we have considered in this paper.  We will consider this further in future work.
